The fundamental shape of dynamic experiences is preserved in episodic memory

### 2018-07-13 main.tex
topic vector word clouds

>>>>

\subsubsection{Topic vector word clouds}
 We created word clouds to visualize the themes contained in the ``hinge-point'' recall events of the model. One component of the topic model comprises a words (???) by topics (100) matrix (R), where the rows represent the weighting of a given word on each topic. Each event (video and recall) was associated with a 1 by 100 topic vector (v) representing the mixture of topics contained in the event. To find words associated with a given event, we computed the dot product between R and v, which gave a 1 by # of words vector where the values represent the `activation' of each of in the event. We normalized these vectors by subtracting the average `activation' across all events. We performed this analysis for each of the line segment model `hinge-points' (i.e. the average recall events connecting the line segments). We also performed this analysis for the video events at the hinge-point locations. Finally, we created word clouds by extracting the top 100 words and plotting them where the size of the word is proportional to its `activation' in the event.
